timesliced_random_cell_selection

### 2018-11-26 src/biological_data_prep.Rmd
minor updates to both background and presence datasets (occurrence coded on background, obs by cell xyzt added to presence)

>>>>

time-sliced by depth

```{r}
obs_cell_yymm_depth <- count(data_aea, c("cell_id", "year", "month", "depthlayerno"))
data_aea <- merge(data_aea, obs_cell_yymm_depth, by.x=c("cell_id", "year", "month", "depthlayerno"), by.y=c("cell_id", "year", "month", "depthlayerno"))
names(data_aea)[names(data_aea)=="freq"] <- "total_cell_obs_xyzt"
```

### 2018-11-26 src/timesliced_random_cell_selection.Rmd
minor updates to both background and presence datasets (occurrence coded on background, obs by cell xyzt added to presence)

    }
}
write.csv(background_all_sp, "../output/bio/background_complete.csv", row.names = FALSE)
background_all <- as.data.frame(background_all_sp)
head(background_all_sp)
```

@@

>>>>

    }
}
write.csv(background_all_sp, "../output/bio/background_complete.csv", row.names = FALSE)
background_all <- as.data.frame(background_all_sp)
head(background_all)
```

@@

# observation occurrence yes or no

create a new column for Occurence, and populate with "0" (because these are all background)
```{r}
background_all$occurrence <- "0"
write.csv(background_all, "../output/bio/background_complete_obs.csv", row.names = FALSE)
head(background_all)
```
